Thesis Draft

### 2015-09-21 main.tex
The Gleaners and I

\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}

@@

\section{Reality of trash (other side of production)}
\subsection{Trash is everywhere and, produced every time}
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession. During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People cares the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using package trash, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. Live with trash. Do not see it as trash actually. Then the question is how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

(Zizek part: talks about ecology at garbage dump in London, and starts with the words "This is where we should start feeling at home." to the ecologist. how ecology turns to ideology and mentions the our wrong perception about the ecology. Draw attention to the event if trash disappears from our world but not world. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonous thing. He claims that it is ideological in the sense that wrong thinking important problems. nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. he asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. we should not forget that we are part of the ecology. we must more alienated from the nature. we must find poetry and spirituality in the dimension of trash. thats the true love of world. Love is not idealization. This part can be extended.)

@@

Getting rid of it is not the significant reaction. It still waits us. Maybe the first thing to do is accept the waste, to accept that there are things out there that serve nothing. To break out of this eternal cycle of functioning.

@@

trash of developed societies has higher recycling period in the nature. higher damage to the nature. hard to reuse. hard to transform. sometimes not to safe to keep them.

\subsubsection{Perspectives of trash from different disciplines}
Trash is ecological problems and it is treats the balance of it. Animals do not aware of plastics materials and eat them. Management problem of municipals.

@@

(Our trash generating behavioral patterns reveals what it is wrong? You are walking outside and entered an coffee shop. buy a coffee inside a paper cup. carried with paper package.)

\subsubsection{How does it become trash?}
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find a way(methodology, approach) to add value to object using artistic methods?)

@@

It can be thought that when the complexity of trashed increased to the effort to repair, reuse and recycle is increase. Therefore for ones that have no such complex tools it is becoming harder to reuse them. In other words objects become more complex their re-usage becomes less likely.

\subsubsection{Types of trashes}
Different production process generates different types of trash.

@@

Agnes varda, the gleaner and I

@@

"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18thcentury Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."

>>>>

\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
\providecommand{\quotes}[1]{``#1''}

@@

\section{Reality of trash (other side of production)}
\subsection{Trash is everywhere and, produced every time}
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession. During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People cares the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. Live with trash. Do not see it as trash actually. Then the question is how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

\subsubsection{The Case of Zizek}
(In documentary film, Examined-life, Zizek talks about ecology at a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonous thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

@@

Getting rid of it is not the significant action. It still waits us at somewhere else or the next generations have to cope with it. (Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing. To break out of this eternal cycle of functioning.

@@

Trash of developed societies has higher decomposing period in the nature. Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.

\subsubsection{Perspectives related with trash from different disciplines}
Trash is ecological problems and it is treats the balance of it. Animals do not aware of plastics materials and eat them. Management problem of municipals.

@@

(Our trash generating behavioral daily consumption patterns \ldots What are the results of them?)

\subsubsection{How does it become trash?}
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

@@

It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase. Therefore for the ones that have no complex tools it is becoming harder to reuse objects. In other words objects become more complex their re-usage becomes less likely.

\subsubsection{Types of trashes}
Different production process generates different types of trash. According to production process, decomposition process\ldots

@@

\subsubsection{The case of \quotes{The Gleaners and I}}
The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning. The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras. This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.

It's a self-reflexive film because the director establish a relationship with the practice of gleaners and her film making practice. Some people gleans crops, the others discarded food, the other baby dolls and Agnès Varda gleans images.

\quotes{Agnès Varda’s film, The Gleaners and I, documents the history and current practice of gleaning in France. Historically, gleaning is the act of collecting leftover crops from farmers’ fields after the harvest. However, in the film Varda expands this definition to include actions that are presently coined \quotes{dumpster diving} where people collect any types of rubbish or unwanted items to reuse them in their own way. Moreover, Varda includes her actions of collecting images with a video camera as gleaning. She is gleaning images. The Gleaners and I far more than document the lives of gleaners. It highlights the degree of global consumerism of the modern world and the ways art can exist within it in relation to gleaning.}

The official subject of this film is gleaning, the act of gathering remnants of crops from a field after the harvest. As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups). More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have closed. And then there’s Varda herself, a gleaner of images, driving around France with a digital camera and a tiny crew (at times, she wields a smaller camera herself, permitting an even greater degree of intimacy).

Making use out of something that has been left behind and labeled as obsolete is not unique to farms and crops. There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely. Seeing the value in what someone else has defined as trash is an art in itself.

Once as a common practice of gleaning throughout the years has evolved, but not disappeared. She keeps light to the modern life gleaners that are not visible every time. One of the interesting thing is here Agnès Varda feels that as a aging person will later become discarded person. In other word we can be subject of the refusal. At some point she become the subject of the thing that she track.

There are many aspects of this documentary film. First draw attention the practice of gleaning. The discarded items that are not fit in the industrial standards because of their shape, color etc. Even if these items are discarded and we are not aware of them, there is also another life for them. Modern life gleaners feed from them. In another words someones trash becomes another trash. There are people live the boundaries of consumption societies. They create their life from the unwanted items. what the society refuses, they find a life or create a life from them. Their lifestyle is also can be seen as alternative to the life on the urban areas with deep relationship with the consumerism. (as also Zizek mentions that love is not idealization. But the industrial processes has some standards and beyond that standards there is not a place for everyone. Life is being lived in the cites is somehow idealized life or tried to be idealized life. beyond the border of the urban there is new life generated. What is not succeed in the cities succeed outside of it.)

She uses unconsciously recorded pieces in the film. \quotes{The last definition of gleaning, gleaning images, ties into what I found both the most amusing and perplexing scene in the film. It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks. She sets this scene to a jazz soundtrack. While watching the scene I was certainly confused. Why is this in here? What does this have to do with gleaning? And certainly why did the scene last so long? But there was also something lovely about it. Maybe it was the music, but for some reasons my senses found it audibly and aesthetically pleasing. I wasn’t able to make much sense out of the meaning behind this scene; I believe Varda referred to it as \quotes{the dance of the lens cap}.  Luckily, Ruth Cruickshank’s article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it. Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest. Varda gleans the image of the dancing lens cap, \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value. Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}. Things that are often forgotten or discarded can easily be revamped to create something useful to someone. The scene was revamped using music and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.}

Refused is not only foods and trash. there are a lot of things that are pushed outside border of the society. She talks and investigates artist that are using discarded items in the artworks. What people not found anything the artist see countless possibilities from them. There is always alternative ways to see something different. Giving life or finding life from discarded life.

The clock found the garbage pile and taken by Agnès Varda. It does not work properly but it has important meaning for her. The time does not go on and it does not remind her that she is aging.

Here another point is that Agnes display images of people picking up things from the ground like their ancestors. Everyone somehow collecting things in their life but particularly she selects these people and their images in action. There should reason for this? For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life. They require it to sustain their life. Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary. What gleaning means become more open (or powerful). It draws a picture of body combination of different parts (connected, dependent to the each other). The reason of gleaning varies but the fact that gleaning is continues in different forms.

She discusses the importance found in the meaning and purpose of art forms like this: \quotes{Varda seeks to encourage viewers to consider what potential agency is demonstrated in the artfulness and contingency of gleaning by individuals excluded\ldots from the homogenizing systems of global consumption} \cite{cruickshank2007work}. One can find more treasure in trash than many of New York’s finest galleries and art exhibits; they bring a grassroots feel to what has always been seen as a stuffy and prude aspect of society.

The Gleaners And I is not an environmental film. Gleaning, Varda implies, can be understood more broadly as a form of resistance, a way of refusing to be boxed in by conventional expectations; as such, it demands that we re-learn age-old skills as well as supply individual creativity and initiative.

The film tracks a series of gleaners as they hunt for food, knicknacks, thrown away items, and personal connection. Varda travels the French countryside as well as the city to find and film not only field gleaners, but also urban gleaners and those connected to gleaners, including a wealthy restaurant owner whose ancestors were gleaners. The film spends time capturing the many aspects of gleaning and the many people who glean to survive. One such person is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants.

Varda's other subjects include artists who incorporate recycled materials into their work, symbols she discovers during her filming (including a clock without hands and a heart-shaped potato), and the French laws regarding gleaning versus abandoned property. Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist. He specializes in reliefs and assemblages made entirely from discarded objects and junk. In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.

@@

"Rubbish theory, a philosophy that attempts to address how value is placed on material objects." "It is a body of thought that addresses how the value of material objects is socially constructed and deconstructed." "An awareness of rubbish theory is important to the understanding of the sociology of consumption and waste because, while what is and is not considered garbage may seem obvious and natural, the value of objects is based on the perceptions of people." "The classic examples of these categories are the durable 18th century Queen Anne tall-boy chest and the transient used automobile." "What decides whether or not something is a durable or transient is often the perceptions of the powerful members of society, those with a vested interest in owning objects whose value will always increase, while the remainder of society owns objects whose value will eventually decrease to nothing."
